---
title: "Ivermectin Strongyloides Meta"
author: Makarand Nadendla
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(meta)
library(metafor)
library(metasens)
library(grid)
library(here)
library(brms)
library(showtext)
library(tidybayes)
library(modelr)
library(tidyverse)
library(extraDistr)
library(shinystan)

iver_raw_dat <- read.csv(here("meta_reg_iver_death.csv"))
font_add_google("Manrope", "mrope")

showtext_auto()
```

Loading and Preparing the Data and calculating Effect Sizes for the Meta Analysis

```{r}
iver_dat <- as_tibble(iver_raw_dat)

# Load the data and calculate the log risk ratios and their respective variances. Then convert to risk ratio and risk ratio standard error
#iver_dat <- iver_dat %>% filter(study != "Hashim", study != "Gonzalez", study != "Okumus")

iver_dat <- iver_dat %>% select(study, country, prevalence_2020, event.e, n.e, event.c, n.c, covid_severity)
#iver_dat <- iver_dat %>% mutate(prevalence_2020 = prevalence_2020/5)
iver_dat <- summary(escalc(ai = event.e,
              n1i = n.e,
              ci = event.c,
              n2i = n.c, measure = "RR", data = iver_dat))
iver_dat <- iver_dat %>% mutate(rr = exp(yi), rr_se = exp(sei))
```
Visualize the data before performing the meta regression to check linearity assumption

```{r}

g<-ggplot(data=iver_dat, aes(x=prevalence_2020,y=exp(yi))) +
  
  labs(title="Ivermectin Treatment: ACM (RR) on Strongyloides Prevalence",x="Strongyloides Prevalence (Parasitological) in Regional Population (Percent)", y="All-Cause Mortality (Log Risk Ratio)") + 
  
  geom_point(aes(size = 1/sei), shape = 21, colour = "black", fill = "darkgray", stroke = 1) +
  
  guides(size = FALSE) +
  
  theme(text = element_text(family = "mrope"), plot.title = element_text(face = "bold",hjust = 0.5))

#png(file = "iverstrongo_lineartrend.png")

#g

#dev.off()

g

```

Running the Bayesian Meta Regression via brms

```{r}
set.seed(42)

# Using brms to construct the model

priors_2 <- c(prior(normal(0,100), class = sd), prior(normal(0,1e6), class = Intercept))

m.brm2 <- brm(yi|se(sei) ~ 1 + prevalence_2020 + (1|study), family = "gaussian",
             data = iver_dat, iter = 4000, prior = priors_2)

pairs(m.brm2)
plot(m.brm2)
fixef(m.brm2)
m.brm2
pp_check(m.brm2)
```
Code for preparing the shinystan object to put on the cloud

```{r}
#as.shinystan.brmfit <- function (brmfit, model.name) {
#draws <- as.array(brmfit)
#sampler_params <- rstan::get_sampler_params(brmfit$fit, inc_warmup = FALSE)
#control <- brmfit$fit@stan_args[[1]]$control
#if (is.null(control)) {
#  max_td <- 10
#} else {
#  max_td <- control$max_treedepth
#  if (is.null(max_td)) {
#    max_td <- 10
#  }
#}
#sso <- shinystan::as.shinystan(
#  X = draws, 
#  model_name = model.name,
#  warmup = 0, 
#  sampler_params = sampler_params, 
#  max_treedepth = max_td,
#  algorithm = "NUTS"
#)
#return (sso)
#}
```

Add the ShinyStan representation of the Bayesian model to the Cloud

```{r}
#m.brm2.shinystan <- as.shinystan.brmfit(m.brm2, model.name = "Ivermectin Treatment: All-Cause Mortality (Log Relative Risk) on Strongyloides Prevalence")
#launch_shinystan(m.brm2.shinystan)
#m.brm2.shinystan <- deploy_shinystan(m.brm2.shinystan, appName = "IvermectinMetaStrongyloides")
```

```{r}

#g<- iver_dat %>%
  
#  data_grid(prevalence_2020 = seq_range(prevalence_2020, n = 10), sei = seq_range(sei, n = 5)) %>%
  
#  add_predicted_draws(m.brm2, re_formula = NA) 

# set seed

set.seed(42)

g_mean <- iver_dat %>%
  
  data_grid(prevalence_2020 = seq_range(prevalence_2020, n = 10), sei = seq_range(sei, n = 5)) %>%
  
  add_epred_draws(m.brm2, ndraws = 200, re_formula = NA)
```

```{r}
#g %>%
#  
#  ggplot(aes(x=prevalence_2020,y=exp(yi))) +
#
#  stat_lineribbon(aes(y = exp(.prediction)), .width = c(.95), color = "#08519C") +
#  
#  geom_point(data = iver_dat, 
#             aes(size = 1/sei), 
#             shape = 21, colour = "black", fill = "darkgray", stroke = 1) +
#  
#  labs(title="Ivermectin Treatment: ACM (RR) on Strongyloides Prevalence",
#       x="Strongyloides Prevalence (Parasitological) in Regional Population (Percent)",
#       y="All-Cause Mortality (Risk Ratio)") + 
#  
#  guides(size = FALSE) +
#  
#  theme(text = element_text(family = "mrope"), 
#        plot.title = element_text(face = "bold",hjust = 0.5)) +
#  
#  scale_fill_brewer()
#
```

Produce the spaghetti plot

```{r}
f <- function(x) exp(fixef(m.brm2)[2]*x+fixef(m.brm2)[1])
g_mean %>%
  # sample 100 means from the posterior
  ggplot(aes(x=prevalence_2020,y=exp(yi))) +
  
  geom_abline(slope = 0, intercept = 1, size = 0.6, linetype="f1") +
  
  geom_line(aes(y = exp(.epred), group = .draw), alpha = 1/10, colour = "#08519C") +
  
  geom_function(data = iver_dat, fun = f, colour = "#08519C", size = 1.3) + 
  
  geom_point(data = iver_dat, 
             aes(size = 1/sei), 
             shape = 21, colour = "black", fill = "darkgray", stroke = 1) + 
  
  
  labs(title="Ivermectin Treatment: ACM (RR) on Strongyloides Prevalence",
       x="Strongyloides Prevalence (Parasitological) in Regional Population (Percent)",
       y="All-Cause Mortality (Risk Ratio)") + 
  
  guides(size = FALSE) +
  
  theme(text = element_text(family = "mrope"), 
        plot.title = element_text(face = "bold",hjust = 0.5)) +
  
  scale_fill_brewer()
```


