---
title: "Ivermectin Strongyloides Meta"
author: Makarand Nadendla
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(meta)
library(metafor)
library(metasens)
library(grid)
library(here)
library(brms)
library(showtext)
library(tidybayes)
library(modelr)
library(tidyverse)
library(extraDistr)
library(shinystan)

iver_raw_dat <- read.csv(here("meta_reg_iver_death.csv"))
font_add_google("Manrope", "mrope")

showtext_auto()


```

Loading and Preparing the Data and calculating Effect Sizes for the Meta Analysis

```{r}
iver_dat <- as_tibble(iver_raw_dat)

# Load the data and calculate the log risk ratios and their respective variances. Then convert to risk ratio and risk ratio standard error
#iver_dat <- iver_dat %>% filter(study != "Hashim", study != "Gonzalez", study != "Okumus")

iver_dat <- iver_dat %>% select(study, country, prevalence_2020, event.e, n.e, event.c, n.c, covid_severity)
#iver_dat <- iver_dat %>% mutate(prevalence_2020 = prevalence_2020/5)
iver_dat <- summary(escalc(ai = event.e,
              n1i = n.e,
              ci = event.c,
              n2i = n.c, measure = "RR", data = iver_dat))
iver_dat <- iver_dat %>% mutate(rr = exp(yi), rr_se = exp(sei))
```

# Visualize the data before performing the meta regression

```{r}
g<-ggplot(data=iver_dat, aes(x=prevalence_2020,y=exp(yi))) +
  
  labs(title="Ivermectin Treatment: ACM (RR) on Strongyloides Prevalence",x="Strongyloides Prevalence (Parasitological) in Regional Population (Percent)", y="All-Cause Mortality (Log Risk Ratio)") + 
  
  geom_point(aes(size = 1/sei), shape = 21, colour = "black", fill = "darkgray", stroke = 1) +
  
  guides(size = FALSE) +
  
  theme(text = element_text(family = "mrope"), plot.title = element_text(face = "bold",hjust = 0.5))

png(file = "iverstrongo_lineartrend.png")

g

dev.off()

g

```

Above and Below Strongyloides Global Prevalence Subgroup Analysis (with Forest Plots)

```{r}
# Forest Plot Calculations

subgroup_iver_dat <- iver_dat %>% mutate(subgroup_div = if_else(prevalence_2020 < 8.1, "Strongyloides Prevalence Below Global Average (<8.1%)", "Strongyloides Prevalence Above Global Average (>8.1%)"))
m.b <- metabin(event.e, n.e, event.c, n.c, 
               data = subgroup_iver_dat,fixed = FALSE, studlab = study, 
#              hakn = TRUE,
                 random = TRUE,
                 method.tau = "REML", 
               subgroup = subgroup_div, 
               tau.common = TRUE,
               sm = "RR", title = "Ivermectin Treatment: ACM (RR) subgrouped on Strongyloides Prevalence")

m.b

# Forest Plot JAMA Style (Figure 2)

#pdf(file = "iverstrongometa_forestplot_jama.pdf", width = 8, height = 7)
png(file = "iverstrongometa_forestplot_jama.png", width = 3000, height = 1500, res = 300)

forest.meta(m.b, layout = "JAMA", leftcols = c("studlab", "event.e", "n.e", "event.c", "n.c", "effect", "ci") ,pooled.events
= TRUE,pooled.totals = TRUE, sortvar = yi ,subgroup.name = "")
#grid.text("Ivermectin Treatment: All-Cause Mortality subgrouped on Strongyloides Prevalence", .5, .822, gp=gpar(cex=1.4))

dev.off()
```

Checking for Publication Bias with Funnel Plots and Other Tests

```{r}
# Publication Bias

# Funnel Plot
col.contour = c("gray95", "gray85", "gray75")
 
png(file = "iverstrongometa_funnelplot.png", width = 3200, height = 1900, res = 300)

funnel.meta(m.b,
            studlab = TRUE,
            #contour = c(0.9, 0.95, 0.99),
            #col.contour = col.contour,
            cex.studlab = 0.6, pos.studlab = 3)

#legend(x = 1.6, y = 0.01, 
#       legend = c("p < 0.1", "p < 0.05", "p < 0.01"),
#       fill = col.contour)

# Add title
title("Funnel Plot (Ivermectin Treatment)")

dev.off()

# Peter's Regression Test
metabias(m.b, method.bias = "peters") #%>%   tbl_regression(include=c("x", "(Intercept)"))

# Harbord Regression Test
harbord.m.b <- metabin(event.e, n.e, event.c, n.c, 
               data = subgroup_iver_dat,fixed = FALSE, studlab = study, 
#              hakn = TRUE,
                 random = TRUE,
                 method.tau = "REML", 
               tau.common = TRUE,
               sm = "RR", title = "Ivermectin Treatment: ACM (RR) subgrouped on Strongyloides Prevalence")
metabias(harbord.m.b, method.bias = "harbord")

```

Meta-Regression Analysis with associated plot (Figure 3)

```{r}

# Run the meta regression with log risk ratios as our outcome, 
m.qual <- rma(ai = event.e,
              n1i = n.e,
              ci = event.c,
              n2i = n.c,
              data = iver_dat,
              mods = ~ prevalence_2020,
              measure = 'RR', 
#              method = "SJ",
#              test="knha", 
              slab = study)

# Observe Study Results
summary(m.qual)

paste0("The percent decrease in relative risk pooled estimate for each 5% increase in strongyloides prevalence is ", (1-round(exp(m.qual$b[2]*5),4))*100,"%  [",(1-round(exp(m.qual$ci.ub[2]*5),4))*100," - ",(1-round(exp(m.qual$ci.lb[2]*5),4))*100, "]")

# Risk Ratio Bubble Plot

png(file = "(RR) Ivermectin Treatment ACM on Strongyloides Prevalence.png", width = 3000, height = 1500, res = 300)

regplot(m.qual, xlab="Strongyloides Prevalence (Parasitological) in Regional Population (Percent)", ylab="All-Cause Mortality (Risk Ratio)",transf=exp ,main = "Ivermectin Treatment: ACM (RR) on Strongyloides Prevalence",refline= 1, legend = TRUE)

dev.off()
```
Checking the confidence intervals of Tau in our model

```{r}
confint(m.qual)
```

Taking a look at the residuals plot for our meta regression. (Figures in Supplement)

```{r}
png(file = "metareg_assumptions.png", width = 3000, height = 1500, res = 300)

# Check Fitted Vs Standardized Residuals for Meta Regression
plot(m.qual)

dev.off()
```

Permutation Test Results

```{r}
# Permutation Test to test whether the results are consistent
# over many different permutations of the data
permutest(m.qual, iter = 10000)
```
